Picky with peakpicking: assessing chromatographic peak quality with simple

### 2023-07-28 manuscript/manuscript.Rmd
Updating to use Bryna's middle initial

---
title: 'Picky with peakpicking: assessing chromatographic peak quality with simple
  metrics in metabolomics'
author: "William Kumler, Bryna Hazelton, and Anitra E. Ingalls"
output:
  word_document:
    reference_docx: template.docx
bibliography: refs.bib
---

@@

WK extracted the Falkor samples, processed the data, performed the analyses, and wrote the manuscript. BH helped design the metrics and implement the regressions as well as providing support and context for the analysis. AEI provided funding and data and helped to interpret the conclusions and edit the manuscript.

>>>>

---
title: 'Picky with peakpicking: assessing chromatographic peak quality with simple
  metrics in metabolomics'
author: "William Kumler, Bryna J. Hazelton, and Anitra E. Ingalls"
output:
  word_document:
    reference_docx: template.docx
bibliography: refs.bib
---

@@

WK extracted the Falkor samples, processed the data, performed the analyses, and wrote the manuscript. BJH helped design the metrics and implement the regressions as well as providing support and context for the analysis. AEI provided funding and data and helped to interpret the conclusions and edit the manuscript.
